---
title: "Sierpinski triangle"
author: "Y. Paulsen"
date: "6/14/2021"
output: html_document
---

The Sierpinski Triangle is a well known fractal... 

The chaos game is...

Pseudocode:
create new_point_1
new_point_2 = midpoint of new_point_1 and a random vertex    
iterate N-times to get points. (N should be large)    
plot points     

   
Set number of sides. 
I will build this program with a triangle in mind, but eventually it should generalize. 

```{r}
sides <- 3
```

Vertices of triangle.   
Eventually replace with call to random locations?   

```{r}
X <- c(0,6,3)
Y <- c(0,0,3*sqrt(3))

vertices <- list(c(0,0), c(6,0), c(3,3*sqrt(3)))
```

Create functions: 

```{r}
# Function: calculate midpoint. 
midpoint <- function(a,b){
  mid <- c();
  mid[1] <- (a[1]+b[1])/2;
  mid[2] <- (a[2]+b[2])/2;
  return(mid)
}

# Function: call random vertex.
ran_vert <- function(sides, vertices){
  z <- sample(sides, 1);
  vertices[[z]]
}
```



```{r}
# Set parameters    
par(mar=c(0,0,0,0), pty="s")   
n <- 10000
plot_points <- list()
plot_points[[1]] <- c(.65,.65)        # Replace starting point with a call to something like `spsample()`

# Generate points to plot  
for(i in 2:n){
  plot_points[[i]] <- midpoint(plot_points[[i-1]], ran_vert(sides, vertices))
}

# Plot points   
plot(X, Y, pch=17, yaxt="n", ylab="", xaxt='n', xlab = "")
for(i in 1:length(plot_points)){
  points(plot_points[[i]][1], plot_points[[i]][2], pch=17)
}
```








