---
title: "Sierpinski triangle"
author: "Y. Paulsen"
date: "6/14/2021"
output: html_document
---

This is just a project I'm working on for fun.  

Create functions: 

```{r}
# Function: calculate distance.  
distance <- function(a,b){
  sqrt((a[1]-b[1])^2+(a[2]-b[2])^2)
}

# Function: calculate midpoint. 
midpoint <- function(a,b){
  mid <- c();
  mid[1] <- (a[1]+b[1])/2;
  mid[2] <- (a[2]+b[2])/2;
  return(mid)
}

# Function: call random vertex.
ran_vert <- function(sides){
  sample(letters[1:sides],1)
}
```

Set number of sides. 
I will build this program with a triangle in mind, but eventually it should be generalizable.  
```{r}
sides <- 3
```

Vertices of triangle.   
Eventually replace with call to random locations. 

```{r}
X <- c(0,6,3)
Y <- c(0,0,3*sqrt(3))

a <- c(0,0)
b <- c(6,0)
c <- c(3,3*sqrt(3))
```

Eventually, replace starting point with a call to something like `spsample()`

```{r}
start_point <- c(1,1)
```


```{r}
move_to <- sample(letters[1:sides],1)
new_point <- midpoint(start_point, move_to)
```

Pseudocode: 

new point1 = midpoint of start and random vertex
new point2 = midpoint of new point1 and random vertex 
iterate 2:N to get remaining points. (N should be large)
plot points  

























