---
title: "Sierpinski triangle"
author: "Y. Paulsen"
date: "6/14/2021"
output: html_document
---

This is just a project I'm working on for fun.  

Create functions: 

```{r}
# Function: calculate midpoint. 
midpoint <- function(a,b){
  mid <- c();
  mid[1] <- (a[1]+b[1])/2;
  mid[2] <- (a[2]+b[2])/2;
  return(mid)
}

# Function: call random vertex.
ran_vert <- function(sides){
z <- sample(sides, 1);
vertices[[z]]
}
```

Set number of sides. 
I will build this program with a triangle in mind, but eventually it should be generalizable. 

```{r}
sides <- 3
```

Vertices of triangle.   
Eventually replace with call to random locations. 

```{r}
X <- c(0,6,3)
Y <- c(0,0,3*sqrt(3))

a <- c(0,0)
b <- c(6,0)
c <- c(3,3*sqrt(3))
vertices <- list(c(0,0), c(6,0), c(3,3*sqrt(3)))
```

Eventually, replace starting point (1,1) with a call to something like `spsample()`

```{r}
n <- 10000
plot_points <- list()
plot_points[[1]] <- c(1,1)

for(i in 2:n){
  plot_points[[i]] <- midpoint(plot_points[[i-1]], ran_vert(sides))
}
#plot_points
```

Pseudocode: 
new point2 = midpoint of new point1 and random vertex 
iterate 1:N to get remaining points. (N should be large)
plot points  

```{r}
plot(X, Y, pch=20)
for(i in 1:length(plot_points)){
points(plot_points[[i]][1], plot_points[[i]][2], pch=20)
}
```








